---
title: "Charting projects by primary commodity against investment risk by Fraser ranking"
output: html_notebook
---

Let's get the MI and Fraser data sets. 



```{r}


library(tidyverse)



library(readr)
overview_dev_status <- read_csv("C:/Users/mmccrae/Desktop/data for projects country fraser apr 18 2018/overview_dev_status.csv")

fraser_prov <- read_csv("C:/Users/mmccrae/Desktop/data for projects country fraser apr 18 2018/fraser_prov.csv")

fraser_country <- read_csv("C:/Users/mmccrae/Desktop/data for projects country fraser apr 18 2018/fraser_country.csv")

overview_dev_status
fraser_prov
fraser_country




```

Let's do some joining


```{r}



joining_prov <- left_join(overview_dev_status,fraser_prov,  by="Province")

joining_country_prorank <- joining_prov %>% plyr::rename(c("Ranking"="ProvRanking"))

joining_country_countryrank <- left_join(joining_country_prorank,fraser_country,  by="Country")


joining_country_countryrank

```


Let's join the two ranking columns

```{r}


master <- joining_country_countryrank %>% replace_na(list(ProvRanking=0)) %>% replace_na(list(Ranking=0)) %>% mutate(FraserRank3=ProvRanking+Ranking) %>% select(-ProvRanking, -Ranking) %>% plyr::rename(c("FraserRank3"="FraserRank"))

master





```


Get rid of zero values in Fraser Rank and Development Status


```{r}

nozero <- master %>% filter(FraserRank!=0) 

View(nozero)

```


Factor activity status. Delete erroneous development status. 

```{r}


nozero$DevelopmentStatus <- NULL

nozero$ActivityStatus <- factor(nozero$ActivityStatus, levels=c("Prospect","Exploration","Advanced Exploration","Preliminary Economic Assessment", "Prefeasibility","Feasibility", "Permitting","Construction","Commissioning","Production","Decommissioning","Closed"))



```

Let's look at the data. Histogram it!



```{r}

ggplot(nozero, aes(ActivityStatus))+
  geom_bar() +stat_count(aes(y=..count..,label=..count..),geom="text",vjust=-1)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(0,13000)



```

Let's look at the data. How about point data? 



```{r}

ggplot(nozero, aes(ActivityStatus, FraserRank, size = ..n..)) + 
  stat_sum(alpha=0.1) +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
 



```

Let's plot

```{r}


ggplot(nozero, aes(ActivityStatus,FraserRank))+
  geom_jitter(height = 0, width=.1, alpha=.1)+
  coord_flip()



```

Plot using a box plot. 


```{r}


ggplot(nozero, aes(ActivityStatus,FraserRank))+
  geom_boxplot(height = 0, width=.1, alpha=.5)+
  coord_flip()




```

Plot using a box plot. This time clean points, data. 


```{r}

boxplot_nozero <- nozero %>% filter(ActivityStatus!="Closed")%>% filter(ActivityStatus!="Decommissioning")


ggplot(boxplot_nozero, aes(ActivityStatus,FraserRank))+
  geom_boxplot(height = 0, width=.1, alpha=.5)+
  ylim(25,100)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))



```


Let's try a faceted density chart

```{r}

library(plyr)


ggplot(nozero, aes(FraserRank)) + 
  geom_density() +
  xlim(0,100) +
  facet_wrap(~ ActivityStatus) 



```

Try running as a geom_point with a trendline


```{r}

boxplot_nozero <- nozero %>% filter(ActivityStatus!="Closed")%>% filter(ActivityStatus!="Decommissioning")


ggplot(boxplot_nozero, aes(ActivityStatus,FraserRank, group=1))+
  geom_jitter(height = 0, width=.1, alpha=.1, na.rm=TRUE)+
  stat_summary(fun.y=mean, colour="red", geom="line", size = 3, na.rm=TRUE)+
  ylim(25,100)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))




```




Try running as a geom_point with a trendline


```{r}

library(Hmisc)

boxplot_nozero <- nozero %>% filter(ActivityStatus!="Closed")%>% filter(ActivityStatus!="Decommissioning")

stat_sum_df <- function(fun, geom="crossbar", ...) {
  stat_summary(fun.data = fun, colour = "red", geom = geom, width = .5, ...)
}


ggplot(boxplot_nozero, aes(ActivityStatus,FraserRank, group=1))+
  geom_jitter(height = 0, width=.1, alpha=.1, na.rm=TRUE)+
  stat_sum_df("mean_cl_boot", mapping = aes(group = 1))+
  ylim(25,100)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))




```




```{r}

ggplot(boxplot_nozero, aes(ActivityStatus,FraserRank, group=1))+
  geom_boxplot(fill="lightblue", group=1, na.rm=TRUE)+
  geom_jitter(height = 0, width=.1, alpha=.1, na.rm=TRUE)+
  ylim(25,100)+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 


```



Taking the best from both worlds.  



```{r}

ggplot(boxplot_nozero, aes(ActivityStatus, FraserRank, group=1)) +
  geom_boxplot(aes(ActivityStatus,FraserRank, group=1),fill="lightblue", group=1, na.rm=TRUE)+
  stat_sum(alpha=0.2) +
  theme_minimal()+
  ylim(25,100)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
 



```
